R Notebook

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
2.9.22 1) Spin up the FML Drive!!!
Getting into the hard part of creating network data

FORMATING SOURCE DATA

2) Only 4 hours of work and 2 committs

---
title: "Social Network Analysis: Week 3: Degree and Centrality"
description: " "
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

@@

      *Week 3 Assignment: Degree and Centrality*

Using the tutorial as a guide, 
      *  you may use your own data; 
      *  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
      *  choose another dataset.

## Working from the example R syntax:
1.   calculate network density; 
2.   degree centrality, and 
3.   centralization measures for your network data.

## Write up your results briefly:
*   focus on interpretation of the results. 
*   Don’t list statistics or provide code, 
*  **the goal is to choose a few interesting results and provide an interpretation.**

## Briefly describe the dataset:
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks. 
Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**

## Provide at least two or three noteworthy results, including:
1.   the relevant statistics and interpretation. 
        For example, explaining which node(s) are most central and which are least central. 
2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
3.   What do you make of network density and centralization measures?  
4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
 5.  Check tutorial for other ideas of results to discuss.

##
1.  [**Identify an existing data set.**]{.ul}

| This can be one provided in the course directory, in an R package or library, located online, or some other source.

2.  [**Briefly describe the network dataset.**]{.ul}

| Identify and describe content of nodes and links, and identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and whether attribute data are present. 
  Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)

# Week 2: Scripts

```{r Import Data Set, echo=TRUE}

  # install.packages("network")

    data("flo", package = "network")

@@

# 2. Briefly describe the network dataset.

@@

```{r Colnames}
 colnames(flo)
```

@@

    -   Flo Format: Size: 16 x 16 square dimmentions indicate a adjacency matrix format

    Network attributes: vertices = 16 directed = TRUE hyper = FALSE loops = FALSE multiple = FALSE bipartite = FALSE total edges= 40 missing edges= 0 non-missing edges= 40

@@

No edge attributes

@@

  dim(flo)

@@

  network(flo)

@@

  summary(flo,
          print.adj = TRUE
          )
```

@@

*Florentine Families Directed Adjacency Matrix Network Objects:*
    **iGraph** flo.ig 
    **Statnet** flo.stat

@@

    flo.stat<-
        network(
        flo,
        directed=F,
        matrix.type="adjacency"
        )

>>>>

---
title: "DRAFT: Week 3: Degree and Centrality"
description: " "
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

@@

## Briefly describe the dataset:
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks.

# Week 2: Scripts
1.  [**Identify an existing data set.**]{.ul}
```{r Set Working Directory, include=FALSE}
getwd()

setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")

@@

```{r Read raw data into R}

library(readr)

index_by_name_Smuggler_Cove_cocktail_recipies <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
    col_names = FALSE, col_types = cols(X1 = col_skip(), 
        X4 = col_skip()), na = "empty")

View(index_by_name_Smuggler_Cove_cocktail_recipies)

summary(index_by_name_Smuggler_Cove_cocktail_recipies)

 # Smuggler's Cove

2. Briefly describe the network dataset.
```{r Identify critical features of data:, echo=FALSE}

dim(smugDrink_Indx.df)
colnames(smugDrink_Indx.df)

@@

```{r Colnames}

@@

@@

@@

  dim(smugDrink_Indx.df)

@@

  network(smugDrink_Indx.df)

@@

  summary(smugDrink_Indx.df,
          print.adj = TRUE
          )
```

@@

*Florentine Families Directed Adjacency Matrix Network Objects:*
    **iGraph** smugDrink_Indx.df.ig 
    **Statnet** smugDrink_Indx.df.stat

@@

    smugDrink_Indx.df.stat<-
        network(
        smugDrink_Indx.df,
        directed=F,
        matrix.type="adjacency"
        )

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.9.22 1) Spin up the FML Drive!!!
Getting into the hard part of creating network data

FORMATING SOURCE DATA

2) Only 4 hours of work and 2 committs

---
title: "DRAFT: Week 3: Degree and Centrality"
description: " "
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, Libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

## Briefly describe the dataset:
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks.

# Week 2: Scripts
1.  [**Identify an existing data set.**]{.ul}
```{r Set Working Directory, include=FALSE}
getwd()

@@

index_by_name_Smuggler_Cove_cocktail_recipies <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
    col_names = FALSE, col_types = cols(X1 = col_skip(), 
        X4 = col_skip()), na = "empty")

View(index_by_name_Smuggler_Cove_cocktail_recipies)

summary(index_by_name_Smuggler_Cove_cocktail_recipies)

@@

@@

2. Briefly describe the network dataset.
```{r Identify critical features of data:, echo=FALSE}

dim(smugDrink_Indx.df)
colnames(smugDrink_Indx.df)

@@

-   *Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)*

1.  *Identify and describe content of nodes and links,*

@@

2.  *Identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and*

@@

  dim(smugDrink_Indx.df)

@@

  network(smugDrink_Indx.df)

@@

  summary(smugDrink_Indx.df,
          print.adj = TRUE
          )
```

@@

*Florentine Families Directed Adjacency Matrix Network Objects:*
    **iGraph** smugDrink_Indx.df.ig 
    **Statnet** smugDrink_Indx.df.stat

@@

    smugDrink_Indx.df.stat<-
        network(
        smugDrink_Indx.df,
        directed=F,
        matrix.type="adjacency"
        )

@@

```
 **Vertex and Edge Attributes**

@@

## Local Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

@@

> Distill is a publication format for scientific and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
##

>>>>

---
title: "R Notebook"
output: html_notebook
---

```{r setup, Libraries, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

@@

## Briefly describe the dataset:

1.  identify initial network format;

2.  describe and identify the nodes including:

    -   how many nodes are in the dataset;

3.  what constitutes a tie or edge including:

    -   how many ties,

    -   whether ties are directed/undirected,

    -   whether ties are weighted/binary,

    -   and how to interpret the value of the tie
        if any.

    -   Whether or not there are edge attributes
        that might be used to:

        -   subset data, or
        -   stack multiple networks.

# Week 2: Scripts

1.  [**Identify an existing data set.**]{.ul}

```{r Set Working Directory, include=FALSE}
getwd()

@@

indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
    col_names = FALSE, col_types = cols(X1 = col_skip(), 
        X4 = col_skip()), na = "empty")

View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

@@

smugDnkIdx_df <- indx_SmugglerCove_recip

@@

2.  Briefly describe the network dataset.

```{r Getting Information on a Dataset:, echo=FALSE}

# list the structure of smugDnkIdx_df
str(smugDnkIdx_df)

# class of an object (numeric, matrix, data frame, etc)
class(smugDnkIdx_df)

# list the variables in smugDnkIdx_df
names(smugDnkIdx_df)

# dimensions of an object
dim(smugDnkIdx_df)
```
#### list the structure of smugDnkIdx_df
$ X2: chr [1:785]
$ X3: chr [1:785]
$ X5: chr [1:785]
$ X6: num [1:785]

cols(
  ..   X1 = col_skip(),
  ..   X2 = col_character(),
  ..   X3 = col_character(),
  ..   X4 = col_skip(),
  ..   X5 = col_character(),
  ..   X6 = col_double()
  .. )

#### class of an object
class(smugDnkIdx_df)
  [1] "spec_tbl_df" 
      "tbl_df"      
      "tbl"         
      "data.frame"

#### list the variables in smugDnkIdx_df
 names(smugDnkIdx_df)
[1] "X2" 
    "X3" 
    "X5" 
    "X6"
#### dimensions of an object
 dim(smugDnkIdx_df)
[1] Rows: 785   
    Cols:   4

# DATA Cleaning
-   rename column names to something memorable
```{r Rename columns}

   # Rename column names

names(smugDnkIdx_df)[1] <- "Drink_Name"
names(smugDnkIdx_df)[2] <- "Ingredient"
names(smugDnkIdx_df)[3] <- "Ingredient_ClassType"
names(smugDnkIdx_df)[4] <- "Drink_Code"

```
-   Drop rows without values 
```{r Remove missing values}

#One-column based criteria: Extract rows where

testData <- smugDnkIdx_df

testData  %>% filter(is.na(Drink_Code))

@@

-   Col X5
    Drop All together
    split varriables into new columns

#
## 1.  *Identify and describe content of nodes and
    links,*

@@

##2.  *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

@@

  dim(smugDnkIdx_df)

@@

  network(smugDnkIdx_df)

@@

  summary(smugDnkIdx_df,
          print.adj = TRUE
          )
```

@@

*Florentine Families Directed Adjacency Matrix
Network Objects:* **iGraph** smugDnkIdx_df.ig
**Statnet** smugDnkIdx_df.stat

@@

    smugDnkIdx_df.stat<-
        network(
        smugDnkIdx_df,
        directed=F,
        matrix.type="adjacency"
        )

@@

**Vertex and Edge Attributes**

@@

## Local Transivity or Clustering

`Local transitivity` (local clustering
coefficient), is a technical description of the
density of an ego network.

@@

> Distill is a publication format for scientific
> and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at
> <https://rstudio.github.io/distill>. ##
